Figures

### 2021-01-28 inst/manuscript/figures.Rmd
Update ignores, figures, validation process script

The preparation of datasets used here and which install with the `activemapper` package, is shown in `data-raw/data_[from|to]_instaces.R`. These are loaded in here.

@@

>>>>

The preparation of datasets used here and which install with the `activemapper` package, is shown in `data-raw/data_[from|to]_instances.R`. These are loaded in here.

@@

```{r, eval=FALSE}
data("label_risk_metrics")

label_risk_metrics %>% 
  filter(Metric != "TSS") %>%  
  ggplot() + geom_point(aes(Risk, Score)) + 
  geom_smooth(aes(Risk, Score), method = "gam") + 
  facet_wrap(~Metric)

label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Precision, Accuracy))

label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Precision, F1))

label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Recall, F1))

label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Precision, Recall))

label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Precision, FPR))
label_risk_metrics %>% select(aoi, Metric, Score) %>% 
  tidyr::pivot_wider(names_from = "Metric", values_from = "Score") %>% 
  ggplot() + geom_point(aes(Recall, FPR))
